### 2022-10-23 article/article.tex
update

\documentclass{article}
\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{R})}}}
\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{T})}}}
\newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
\newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
\newcommand{\eet}{\epsilon_{e\tau}}
\newcommand{\eem}{\epsilon_{e\mu}}
\newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
\newcommand{\ep}{\ensuremath{\epsilon^\prime}}
\renewcommand{\ne}{\nu_e}
\newcommand{\Ereco}{E^{R}}
\newcommand{\Etrue}{E^{T}}
\newcommand{\nm}{\nu_\mu}
\newcommand{\ab}{\alpha\beta}
\newcommand{\nt}{\nu_\tau}
\newcommand{\ane}{\bar\nu_e}
\newcommand{\anm}{\bar\nu_\mu}               
\newcommand{\ant}{\bar\nu_\tau}
\newcommand{\dm}{\Delta m^2_{31}}
\newcommand{\sth}{\sin^2(2\theta_{23})}

\newcommand{\Pee}{P_{e  e}}
\newcommand{\Pem}{P_{e  \mu}}
\newcommand{\Pet}{P_{e  \tau}}

@@

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\section{Formalism of non-standard interactions}\label{sec:intro} %OK
Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions not considered in the Standard Model.
We consider matter NSIs arising from the neutral current NSIs, which exclude production 
and detection effects. An effective four-fermion Lagrangian for this type of interaction can be written as
\begin{align}
   \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align}
where NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$, and $P_X$ is the chirality projection operators with $X \in \{L,R\}$.

For chirality $X$, the NSI Hamiltonian takes the form 
\begin{align}
   H &= \frac{1}{2E} UM^2U^\dagger + \sqrt{2}G_F n_e \text{diag}(1,0,0) + \sqrt{2}G_F \sum_f n_f \epsilon^{fX}
\end{align}

We have no independent sensitivity for the chirality of $\epsilon^{fX}$, so we sum over these to obtain the vectorial parameter as $\epsilon^{fV}_{\alpha\beta} = \epsilon^{fL}_{\alpha\beta}+ \epsilon^{fR}_{\alpha\beta}$.
Moreover, we normalize the fermion number density $n_f$ by
the electron number density $n_e$. Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
so we use the relations $n_u/n_e \simeq n_d/n_e \simeq 3$.
The effective NSI parameters in matter now take the form
\begin{align} \label{eq:epsilon}
    \epsilon_{\alpha\beta} &= \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
                           &= \sum_X \epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})
\end{align}
We note that our definition of $\epsilon_{\alpha\beta}$ differs from e.g. \cite{deepcoreNSI}, where the quark number density is used to normalize
the parameters.

@@

To propagate the neutrino states through the Earth, we solve the Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}. 
The Earth density profile is taken from the PREM~\cite{PREM}, and we do not consider neutrino absorption.
The baseline for a given trajectory is determined using an average neutrino production height of 15 km and an Earth radius of 6371 km.
Thus, matter oscillations introduce a zenith angle dependence in two areas. Firstly, the matter potential depends on the matter density through the
neutrino propagates. A neutrino with $\cos{\theta_z} < -0.87$ will traverse through the dense Earth core, whereas a mantle-crossing neutrino 
with $\cos{\theta_z} > -0.87$ will not. Secondly, the zenith angle also alters the baseline through which a neutrino undergoes matter oscillations.
After this, we are ready to study the NSI effect on probability level.

\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects} %OK
% Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
% However, for the purpose of qualitatively elucidating the NSI effect in this subsection, we take the effective area of $\nm$ and $\anm$ to be equal. 
% Thus, we simply add the neutrino to the antineutrino contributions in both Fig.~\ref{fig:nsi_probs} and Fig.~\ref{fig:flux_ratio}.

% In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
% with some also shifting the probability in the stationary region above \SI{100}{\GeV}.
% This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
% (e.g. $\eem$ and $P_{\mu\mu}$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
% which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
% the three different effects in Fig.~\ref{fig:nsi_probs}.

@@

The atmospheric $\nm \to \nt$ transition will be the most abundant, making $\emt$, $\emm$, $\ett$ the most suitable
NSI parameters to constrain from muon events. As we will see, $\eem$ is also a good candidate to constrain, albeit a weaker one.

In Fig.~\ref{fig:emt_ett_probs}, we see how the introduction of $\emt = 0.02$ alters the $\nm$ and $\anm$ survival probabilities
for neutrinos that traverse the entire Earth diameter (i.e. $\ztrue = -1$). $\emt$ does not dramatically change neither
amplitude nor frequency of the probabilities. Instead, it seems to stretch or compress the oscillations. Since the 
only difference between the way neutrinos and antineutrinos interact with matter is the sign of the potential, the probability for
$\nm$ with positive $\epsilon_{\alpha\beta}$ is identical to the probability for $\anm$ with negative $\epsilon_{\alpha\beta}$. Thus, the dashed line 
in the right panel not only shows the survival probability for $\anm$ with $\emt=0.02$, but also the survival probability for $\nm$ with $\emt=-0.02$.
Hence, we note that $\emt > 0$ stretches (compresses) $\Pmm$ for neutrinos (antineutrinos), while $\emt < 0$ compresses (stretches) $\Pmm$ for neutrinos (antineutrinos).

The value of $\ett$ affects neither $\Pmm$ nor $\Pamam$, in the IceCube region above \SI{500}{\GeV}. Hence, we will not be able
to say anything about $\ett$ in our IceCube study.  Comparing the probabilities in Fig.~\ref{fig:emt_ett_probs} with $\ett = 0.05$ with the ones for $\emt = 0.02$ in Fig.~\ref{fig:emt_ett_probs},
we see that even though we let $\ett$ take 2.5 times the value of $\emt$, its effect on $\Pmm$ is smaller. The weakening of the $\Pamam$ resonance will be visible in DeepCore, but we should expect a less stringent 
constraint due to the weakness of the effect compared to $\emt$.

Thus, we will use IceCube to constrain $\emt$ only.

Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The exception of this lies 
in the DeepCore region of rapid oscillations, where mixing is more violent. 
\begin{figure}
    \begin{center}
        \includegraphics[width=0.99\textwidth]{figures/Pmm_emt_probs.pdf}
        \includegraphics[width=0.99\textwidth]{figures/Pmm_ett_probs.pdf}
        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero. In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$. At \si{\TeV} energies, both probabilities simply get shifted down, resulting in a net reduction of track events.
        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero. $\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study. However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
        \label{fig:emt_ett_probs}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics[width=0.99\textwidth]{figures/eem_probs.pdf}
        \includegraphics[width=0.99\textwidth]{figures/eet_probs.pdf}
        \caption{Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$. \emph{Top panel:} $\eem = 0.2$. All other NSI parameters are fixed to zero. Instead of the oscillations shifting to the left or right, $\eem$ dampens an oscillation peak for low \si{\GeV}. At \si{\TeV}, the probability is shifted down, just as with $\emt$.
        \emph{Bottom panel:} $\eet = 0.2$. All other NSI parameters are fixed to zero. Here, we see a very weak shifting and a $\nm$ weaker dip at low \si{\GeV}, and again, no visible effect at \si{TeV} energies. }
        \label{fig:eem_eet_probs}
    \end{center}
\end{figure}

\begin{figure}% TODO: check if this is redundant
   \includegraphics[width=0.85\textwidth]{figures/probabilities.pdf}
   \caption{}\label{fig:nsi_probs}
\end{figure}

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{figures/Pee_eet_probs.pdf}
        \caption{Electron neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero. Here we see a strong difference across the whole energy range, in contrast to the $\nm$ and $\anm$ plots in Fig~\ref{fig:eem_eet_probs}.}
        \label{fig:Pee_eet_probs}
    \end{center}
\end{figure}

@@

For $\eet$, we see a similar effect on the dip in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
see the $\eet$ effect in DeepCore/PINGU. Remember that we now have the option to look at the other flavor channels than $\mu$ since we 
have cascade events for DeepCore and PINGU. If we simulate 
$\Pme^{NSI}$ at three different energies, and let both $\eem$ and $\eet$ vary together between the values $\{-0.3,0.3\}$, we produce a two-dimensional grid of probabilities.
Subtract the regular $\Pme^{SI}$ (that is, no NSI), and take the absolute value of the difference. We see the result in Fig.~\ref{fig:eem_eet_prob}. 
The middle and right panels, which show the absolute probability difference at \si{25} and $\SI{50}{\GeV}$, respectively, are very bleak,
indicating that the impact of the NSI parameters $\eem$ and $\eet$ is not as strong at these energy levels. Turning to the left-most panel,
we see a region in which the difference again is close to zero, but now surrounded by fringes of very large differences, up to $50\%$ difference 
in the $\Pme$ probability. This indicates that the NSI parameters are much more influential at these energies, and that we should be able to 
constrain both $\eem$ and $\eet$ from $\SI{5}{\GeV}$ cascade events.

\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{figures/eem_eet_prob.pdf}
    \caption{The quantity $\abs{P_{\mu e}^{NSI} - P_{\mu e}^{SI}}$ when we let $\eem$ and $\eet$ independently vary over
    the range \{-0.3,0.3\} at \si{5}, \si{25}, and $\SI{50}{\GeV}$. At $\SI{5}{\GeV}$, we see strong deviations in the probabilities, showing
    a promising indication that constriction of $\eem$ and $\eet$ is possible using cascade events at these energies.}\label{fig:eem_eet_prob}
\end{figure}

\subsection{NSI phenomenology at flux level}\label{sec:nsiFluxEffects}
To study the NSI flux effect, we propagate the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth.
The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
\begin{align}\label{eq:propFlux}
    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
\end{align}
where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$.
To illustrate the impact of $\emt$ at flux level, 
we plot in Fig.~\ref{fig:flux_ratio} the quantity $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$, 
where all fluxes are propagated to detector level by Eq.~\ref{eq:propFlux}. 
In the left (right) panel, we plot the flux in region in which 99\% of the 
DeepCore (IceCube) track events originating from $\nm + \anm$ fluxes are contained. We see that the only clear signal discernible to the IceCube detector
is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
is exposed to multiple fringes of flux surpluses with a factor in the order of $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
energy-independent but zenith-sensitive IceCube deficiency.
%TODO: check values above after final plot of flux ratios

@@

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.8\linewidth]{figures/flux_ratio.pdf}
   \end{center}
   \caption{Ratio of detector NSI to SI atmospheric $\nu_\mu + \bar{\nu}_\mu$ fluxes expressed as $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$.
   We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
   Left (right) panel shows the flux ratio in the energy range in which 99\% of the simulated DeepCore (IceCube) events are contained.
   }\label{fig:flux_ratio}
\end{figure}

@@

The event count for each bin reads
\begin{align}\label{eq:ICevents}
    N_{ij} &= T \sum_\beta\int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r 
    \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \phi_\beta^\text{det}  A^\text{eff}_\beta \dd E^t
    \,,
\end{align}
where $T$ is the live time of the detector, $\beta$ the final neutrino flavors, $\theta_z^r$ the reconstructed 
zenith angle, i.e.~the deduced direction of the incoming neutrino binned with index $i$. $\theta^t_z$ is the true zenith angle of the incoming neutrino. 
$E^r$ is the reconstructed energy, binned with index $j$. $R(\theta^r,\theta^t)$ is a zenith resolution function 
that describes the relationship with the reconstructed and true zenith angles, specific to the 86-string configuration of IceCube.
$R(E^r,E^t)$ is an energy resolution function 
that describes the relationship with the reconstructed and true energies. $\phi_\beta^\text{det}$ is the conventional atmospheric neutrino flux for flavor $\beta$, propagated to detector level
in accordance with Eq.~\ref{eq:propFlux}. The effective area $A^\text{eff}$ is binned and provided to us by the IceCube collaboration~\cite{ICaeff}.

>>>>

\documentclass{revtex4-2}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

% True/reconstructed parameters
\newcommand{\z}{\ensuremath{\cos{(\theta_z)}}}
\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{R})}}}
\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{T})}}}
\newcommand{\treco}{\ensuremath{\theta_z^{R}}}
\newcommand{\ttrue}{\ensuremath{\theta_z^{T}}}
\newcommand{\xreco}{\ensuremath{x^R}}
\newcommand{\xtrue}{\ensuremath{x^T}}
\newcommand{\Ereco}{E^{R}}
\newcommand{\Etrue}{E^{T}}

% NSI parameters
\newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
\newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
\newcommand{\eet}{\epsilon_{e\tau}}
\newcommand{\eem}{\epsilon_{e\mu}}
\newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
\newcommand{\ep}{\ensuremath{\epsilon^\prime}}

% Oscillation parameters
\newcommand{\dm}{\Delta m^2_{31}}
\newcommand{\sth}{\sin^2(2\theta_{23})}

% Neutrinos
\renewcommand{\ne}{\nu_e}
\newcommand{\nm}{\nu_\mu}
\newcommand{\ab}{\alpha\beta}
\newcommand{\nt}{\nu_\tau}
\newcommand{\ane}{\bar\nu_e}
\newcommand{\anm}{\bar\nu_\mu}               
\newcommand{\ant}{\bar\nu_\tau}

% Probabilities
\newcommand{\Pee}{P_{e  e}}
\newcommand{\Pem}{P_{e  \mu}}
\newcommand{\Pet}{P_{e  \tau}}

@@

\begin{document}
\section{Formalism of non-standard interactions}\label{sec:intro}
Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions not considered in the Standard Model.
We consider matter NSIs arising from the neutral current NSIs, which exclude production 
and detection effects. An effective four-fermion Lagrangian for this type of interaction can be written as
\begin{align}
   \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align}
where NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$, and $P_X$ is the chirality projection operators with $X \in \{L,R\}$.

For chirality $X$, the NSI Hamiltonian takes the form 
\begin{align}
   H &= \frac{1}{2E} UM^2U^\dagger + \sqrt{2}G_F n_e \text{diag}(1,0,0) + \sqrt{2}G_F \sum_f n_f \epsilon^{fX}\,,
\end{align}
where $U$ is the PMNS matrix, $M^2$ the matrix containing matter-squared differences, and $n_f$ the fermion number density
of fermion $f$.
We have no independent sensitivity for the chirality of $\epsilon^{fX}$, so we sum over these to obtain the vectorial parameter as $\epsilon^{fV}_{\alpha\beta} = \epsilon^{fL}_{\alpha\beta}+ \epsilon^{fR}_{\alpha\beta}$.
Moreover, we normalize $n_f$ by
the electron number density $n_e$. Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
so we use the relations $n_u/n_e \simeq n_d/n_e \simeq 3$.
The effective NSI parameters in matter now take the form
\begin{align} \label{eq:epsilon}
    \epsilon_{\alpha\beta} &= \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
                           &= \sum_X \epsilon_{\ab}^{eX} + 3(\epsilon_{\ab}^{uX} + \epsilon_{\ab}^{dX})
\end{align}
We note that our definition of $\epsilon_{\alpha\beta}$ differs from e.g. \cite{deepcoreNSI}, where the quark number density is used to normalize
the parameters.

@@

To propagate the neutrino states through the Earth, we solve the Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}. 
The Earth density profile is taken from the PREM~\cite{PREM}, and we do not consider neutrino absorption.
The baseline for a given trajectory is determined using an average neutrino production height of 15 km and an Earth radius of 6371 km.
Thus, matter oscillations introduce a zenith angle dependence in two areas. Firstly, the matter potential depends on the matter density through the
neutrino propagates. A neutrino with indident zenith angle $\theta_z$ having $\z < -0.87$ will traverse through the dense Earth core, whereas a mantle-crossing neutrino 
with $\z > -0.87$ will not. Secondly, the zenith angle also alters the baseline through which a neutrino undergoes matter oscillations.
After this, we are ready to study the NSI effect on probability level.

\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects}
% Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
% However, for the purpose of qualitatively elucidating the NSI effect in this subsection, we take the effective area of $\nm$ and $\anm$ to be equal. 
% Thus, we simply add the neutrino to the antineutrino contributions in both Fig.~\ref{fig:nsi_probs} and Fig.~\ref{fig:flux_ratio}.

% In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
% with some also shifting the probability in the stationary region above \SI{100}{\GeV}.
% This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
% (e.g. $\eem$ and $\Pmm$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
% which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
% the three different effects in Fig.~\ref{fig:nsi_probs}.

@@

The atmospheric $\nm \to \nt$ transition is the most abundant, making $\emt$, $\emm$, $\ett$ the most suitable
NSI parameters to constrain from muon events. As we will see, $\eem$ is also a good candidate to constrain, albeit a weaker one.

In Fig.~\ref{fig:emt_ett_probs}, we see how the introduction of $\emt = 0.02$ alters the $\nm$ and $\anm$ survival probabilities
for neutrinos that traverse the entire Earth diameter (i.e. $\z = -1$). $\emt$ does not dramatically change neither
amplitude nor frequency of the probabilities. Instead, it seems to stretch or compress the oscillations. Since the 
only difference between the way neutrinos and antineutrinos interact with matter is the sign of the potential, the probability for
$\nm$ with positive $\epsilon_{\alpha\beta}$ is identical to the probability for $\anm$ with negative $\epsilon_{\alpha\beta}$. Thus, the dashed line 
in the right panel not only shows the survival probability for $\anm$ with $\emt=0.02$, but also the survival probability for $\nm$ with $\emt=-0.02$.
Hence, we note that $\emt > 0$ stretches (compresses) $\Pmm$ for neutrinos (antineutrinos), while $\emt < 0$ compresses (stretches) $\Pmm$ for neutrinos (antineutrinos).

The value of $\ett$ affects neither $\Pmm$ nor $\Pamam$, in the IceCube region above \SI{500}{\GeV}. Hence, we will not be able
to say anything about $\ett$ in our IceCube study.  Comparing the probabilities in Fig.~\ref{fig:emt_ett_probs} with $\ett = 0.05$ with the ones for $\emt = 0.02$ in Fig.~\ref{fig:emt_ett_probs},
we see that even though we let $\ett$ take 2.5 times the value of $\emt$, its effect on $\Pmm$ is smaller. The weakening of the $\Pamam$ resonance will be visible in DeepCore, but we should expect a less stringent 
constraint due to the weakness of the effect compared to $\emt$. Thus, we will use IceCube to constrain $\emt$ only.

Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The exception of this lies 
in the DeepCore region of rapid oscillations, where mixing is more violent. 
\begin{figure} %TODO: maybe add shaded region > 500 GeV to signify IC limit
    \begin{center}
        \includegraphics[width=0.9\textwidth]{figures/Pmm_emt_probs.pdf}
        \includegraphics[width=0.9\textwidth]{figures/Pmm_ett_probs.pdf}
        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
        $\z = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero. In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$. At \si{\TeV} energies, both probabilities simply get shifted down, resulting in a net reduction of track events.
        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
        $\z = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero. $\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study. However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
        \label{fig:emt_ett_probs}
    \end{center}
\end{figure}

\begin{figure} %TODO: maybe add shaded region > 500 GeV to signify IC limit
    \begin{center}
        \includegraphics[width=0.9\textwidth]{figures/eem_probs.pdf}
        \includegraphics[width=0.9\textwidth]{figures/eet_probs.pdf}
        \caption{Muon neutrino and antineutrino survival probabilities for
        $\z = -1$. \emph{Top panel:} $\eem = 0.2$. All other NSI parameters are fixed to zero. Instead of the oscillations shifting to the left or right, $\eem$ dampens an oscillation peak for low \si{\GeV}. At \si{\TeV}, the probability is shifted down, just as with $\emt$.
        \emph{Bottom panel:} $\eet = 0.2$. All other NSI parameters are fixed to zero. Here, we see a very weak shifting and a $\nm$ weaker dip at low \si{\GeV}, and again, no visible effect at \si{TeV} energies. }
        \label{fig:eem_eet_probs}
    \end{center}
\end{figure}

%\begin{figure} %This one might be redundant with Fig 1 and 2
%   \includegraphics[width=0.85\textwidth]{figures/probabilities.pdf}
%   \caption{}\label{fig:nsi_probs}
%\end{figure}

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=0.8\textwidth]{figures/Pee_eet_probs.pdf}
        \caption{Electron neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero. 
        Here we see a strong difference across the whole energy range, in contrast to the $\nm$ and $\anm$ plots in Fig~\ref{fig:eem_eet_probs}.}
        \label{fig:Pee_eet_probs}
    \end{center}
\end{figure}

@@

For $\eet$, we see a similar effect on the dip in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
see the $\eet$ effect in DeepCore/PINGU. Remember that we now have the option to look at the other flavor channels than $\mu$ since we 
have cascade events for DeepCore and PINGU. If we simulate 
$\Pme^{NSI}$ at three different energies, and let both $\eem$ and $\eet$ vary together between the values $\{-0.3,0.3\}$, we produce a two-dimensional grid of probabilities.
Subtract the regular $\Pme^{SI}$ (i.e, $\Pme$ under standard interactions), and take the absolute value of the difference. We see the result in Fig.~\ref{fig:eem_eet_prob}. 
The middle and right panels, which show the absolute probability difference at \si{25} and $\SI{50}{\GeV}$, respectively, are very bleak,
indicating that the impact of the NSI parameters $\eem$ and $\eet$ is not as strong at these energy levels. Turning to the left-most panel,
we see a region in which the difference again is close to zero, but now surrounded by fringes of very large differences, up to $50\%$ difference 
in the $\Pme$ probability. This indicates that the NSI parameters are much more influential at these energies, and that we should be able to 
constrain both $\eem$ and $\eet$ from $\SI{5}{\GeV}$ cascade events.

\begin{figure}
    \centering
    \includegraphics[width=0.99\textwidth]{figures/eem_eet_prob.pdf}
    \caption{The quantity $\abs{P_{\mu e}^{NSI} - P_{\mu e}^{SI}}$ when we let $\eem$ and $\eet$ independently vary over
    the range \{$-0.3$, $0.3$\} at \si{5}, \si{25}, and $\SI{50}{\GeV}$. At $\SI{5}{\GeV}$, we see strong deviations in the probabilities, showing
    a promising indication that constriction of $\eem$ and $\eet$ is possible using cascade events at these energies.}\label{fig:eem_eet_prob}
\end{figure}

\subsection{NSI phenomenology at flux level}\label{sec:nsiFluxEffects}
To study the impact of NSI on the flux, we propagate the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth.
The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
\begin{align}\label{eq:propFlux}
    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
\end{align}
where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$.
To illustrate the impact of $\emt$ at flux level, 
we plot in Fig.~\ref{fig:flux_ratio} the quantity $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$, 
where all fluxes are propagated to detector level by Eq.~\ref{eq:propFlux}.
In the left (right) panel, we plot the flux in region in which 99\% of the 
DeepCore (IceCube) track events originating from $\nm + \anm$ fluxes are contained. We see that the only clear signal discernible to the IceCube detector
is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\z < -0.87$. DeepCore on the other hand, 
is exposed to multiple fringes of flux surpluses with a factor in the order of $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
energy-independent but zenith-sensitive IceCube deficiency.
%TODO: check values above after final plot of flux ratios

@@

\begin{figure}[!tb] %TODO: remove "true" in zenith x axis label?
   \begin{center}
      \includegraphics[width=0.99\linewidth]{figures/flux_ratio.pdf}
   \end{center}
   \caption{Ratio of atmospheric $\nu_\mu + \bar{\nu}_\mu$ fluxes at detector level, expressed as the logarithm of $(\phi_{\nu_\mu}^{NSI} + \phi_{\bar\nu_\mu}^{NSI})/(\phi_{\nu_\mu}^{SI} + \phi_{\bar\nu_\mu}^{SI})$.
   For the NSI fluxes $\phi^\text{NSI}$, we set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. For the SI fluxes $\phi^\text{SI}$, all $\epsilon_{\alpha\beta} = 0$.
   Left (right) panel shows the flux ratio in the energy range in which 99\% of the simulated DeepCore (IceCube) events are contained.
   }\label{fig:flux_ratio}
\end{figure}

@@

The event count for each bin reads
\begin{align}\label{eq:ICevents}
    N_{ij} = T \sum_\beta &\int_{(\zreco)_i}^{(\zreco)_{i+1}} \dd \zreco \int_{\Ereco_{j}}^{\Ereco_{j+1}} \dd \Ereco \times \nonumber \\
    \times &\int_0^\pi R(\treco,\ttrue) \dd \ztrue \int_0^\infty R(\Ereco,\Etrue) \phi_\beta^\text{det}  A^\text{eff}_\beta \dd \Etrue
    \,,
\end{align}
where $T$ is the live time of the detector, $\beta$ the final neutrino flavors, $\treco$ the reconstructed 
zenith angle, i.e.~the deduced direction of the incoming neutrino binned with index $i$. $\ttrue$ is the true zenith angle of the incoming neutrino. 
$\Ereco$ is the reconstructed energy, binned with index $j$. $R(\treco,\ttrue)$ is a zenith resolution function 
that describes the relationship with the reconstructed and true zenith angles, specific to the 86-string configuration of IceCube.
Similarily, $R(\Ereco,\Etrue)$ is the resolution function for the energy relationships. $\phi_\beta^\text{det}$ is the conventional atmospheric neutrino flux for flavor $\beta$, propagated to detector level
in accordance with Eq.~\ref{eq:propFlux}. The effective area $A^\text{eff}$ is binned and provided to us by the IceCube collaboration~\cite{ICaeff}.

For the energy and zenith resolution functions, we assume a log-normal distribution, giving it the form 
\begin{align}
    R(\xreco, \xtrue) = \frac{1}{\sqrt{2\pi} \sigma_{\xreco}\xreco} \exp\left[-\frac{(\log \xreco-\mu(\xtrue))^2}{2\sigma_{\xreco}^2}\right]\,.
\end{align}
However, the energy reconstruction is biased, meaning that the most probable reconstructed energy for a given true energy is not the same due to 
systematic differences~\cite{weaverThesis}. Thus, we don't assume that $\mu(\Etrue) =\Ereco$. 
To model this relationship between $\Etrue$ and $\Ereco$, we fit a Gaussian process regressor on the IC-86 Monte Carlo dataset from~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $\Ereco$. We then take the $\Etrue$ points of the 99th percentile of each reconstructed
distribution to obtain the $\Etrue$ limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
events is less than $\SI{2}{\degree}$, making $\ztrue$ practically coincide with $\zreco$ for our study~\cite{IC2020}.
